---
title: "Effect of gene expression on invasion of K27me3/K9me3"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(reshape2)
library(tidyverse)
library(reactable)
library(data.table)
```

---

# Gene body plots {.tabset}

The lowest expression quartile seems to be most affected by K27me3 and K9me3, with changes in DNA methylation also found in these genes.

Besides K36me2/3 which are normalized by mass-spec, these signals are only library depth-normalized (CPM). 

## K36me2
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/gene_body_plots/K36me2", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K36me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/gene_body_plots/K36me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## DNAme
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/gene_body_plots/DNAme", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K27me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/gene_body_plots/K27me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K9me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/gene_body_plots/K9me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

---

# Gene body plots divided into exons/introns {.tabset}

Examining changes in more detail within exons and introns for the lowest expression quantile

## K36me2
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/first_quantile_exon_intron/K36me2", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K36me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/first_quantile_exon_intron/K36me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## DNAme
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/first_quantile_exon_intron/DNAme", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K27me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/first_quantile_exon_intron/K27me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K9me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/first_quantile_exon_intron/K9me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

---

# Promoters {.tabset}

Taking the promoters of the lowest expression quartile, we can examine the levels of the various histone marks as well as DNA methylation.

## K36me2
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/promoters/K36me2", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K36me3
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/promoters/K36me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## DNAme
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/promoters/DNAme", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## ATACseq
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/promoters/ATACseq", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K27me3
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/promoters/K27me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K9me3
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/all_histone_marks/promoters/K9me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

