---
title: "Mass spec results"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(reshape2)
library(tidyverse)
library(reactable)
library(data.table)
```

---

# K36me
```{r,K36me,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/K36me/mass_spec", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# K27me
<ul>
  <li>There is a decrease in K27me1 following K36me2 depletion, with a corresponding increase in K27me2 and more substantially in K27me3, likely due to the lowest K27me state (me1) being upgraded to higher orders of methylation. </li>
</ul>

```{r,K27me,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/K27me_mass_spec", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# K4me
<ul>
  <li>Following K36me2 depletion, there is a trend for increasing K4me. </li>
  <li>Interestingly, there is a decrease in K4me2 following SETD2-KO. However, it could be that something went wrong for these samples during mass-spec. For these two samples, the values are 0.0001% and 0.0004% H3K4me2-marked histones respectively. </li>
  <li>Additionally, there appears to be a decrease in K4me3 following NSD3-KO although there is quite a lot of variability with respect to the replicates. Perhaps a more targeted PRM for K4me3 or western blotting to verify some of these results would be helpful. </li>
</ul>

```{r,K4me,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/K4me/mass_spec", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# K9me
```{r,ms_K9me,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/K9me3/mass_spec", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

