---
title: "PTM signal centered on ATAC-seq peaks"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(reshape2)
library(tidyverse)
library(reactable)
library(data.table)
```

---

# Heatmaps and aggregate plots
</ul>
<li> These heatmaps and aggregate plots were centered on an <b> intersect </b> of ATAC-seq peaks between TKO and QKO - i.e. only ATAC-seq peaks found in both cell lines were used. </li>
<li> Then, only a subset of ATAC-seq peaks were used, specifically those overlapping promoters and those overlapping enhancers by at least 1 bp. </li>
<li> Unfortunately, we still do not have H3K27me3 or H3K4me1/3 for QKO, hence I used DKO and QKO_PGK_NSD3_OE as proxies for H3K4me1. </li>
</ul>
```{r,hm,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/10T_downstream/pushed_images/all_histone_marks/centered_on_ATACpeaks/hm", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

```{r,ag,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/10T_downstream/pushed_images/all_histone_marks/centered_on_ATACpeaks/ag", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

---

