---
title: "TE analysis"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(reshape2)
library(tidyverse)
library(reactable)
library(data.table)
```

---

# TE subfamilies {.tabset}

<b> Processing and filtering steps </b>
<ul>
  <li> TEs that overlap both cluster A and B domains are excluded from these analyses.</li>
  <li> Only TEs found at intergenic regions and with FPKM > 1 are included.</li>
  <li> NSD3-unedit and two unedited clones of NSD1-KO are used for comparison.</li>
  <li> TEs within 10kb upstream and downstream of genes are excluded </li>
  <li> TEs are grouped within their respective sub-families </li>
  <li> Exclusive subfamilies are filtered by at least 3 members of the subfamily having signifcant fold change in the positive or negative direction </li>
  <li>Significantly regulated subfamilies were filtered using abs(log2FC) > 1 and padj < 0.05. </li>
</ul>

<b> Notable genome-wide observations </b>
<ul>
  <li>More TE subfamilies within the family <b>ERVK</b> tend to be upregulated than downregulated genome-wide regardless of whether they are found in cluster A or cluster B regions.</li>
</ul>

## TE subfamilies within clusB {.tabset}

<ul>
  <li>About 2 fold more TE subfamilies become upregulated in cluster B regions following TKO. Exclusively in these cluster B domains, more TE subfamilies in <b> ERVL-MaLR and L1 </b> become significantly upregulated than downregulated.</li>
</ul>

### Volcano
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/Analyzing_K9me3_loss/TE_expression/within_clusB/volcano/TE_subfamilies", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### TE subfamily counts
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/Analyzing_K9me3_loss/TE_expression/within_clusB/subfamily_counts", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## TE outside clusB {.tabset}

<ul>
  <li>A similar number of TE subfamilies become up- and downregulated in cluster A regions. Exclusively within cluster A regions, however, TE families of <b> ERVL-MaLR and L1 </b> become downregulated. </li>
</ul>

### Volcano {.tabset}

#### abs(log2FC) > 0
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/Analyzing_K9me3_loss/TE_expression/outside_clusB/volcano/TE_subfamily/logFC_0", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

#### abs(log2FC) > 1
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/Analyzing_K9me3_loss/TE_expression/outside_clusB/volcano/TE_subfamily/logFC_1", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### TE subfamily counts
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_downstream/pushed_images/Analyzing_K9me3_loss/TE_expression/outside_clusB/TE_subfamily_counts", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

---
